---
title: " The ability to detect walking instantaneous frequency using acceleration data from wrist-worn wearable sensors in stroke patient. "
author: "Camille_LAMBERT"
co-authors: "Claude IA and Copilot IA"
date: "2026-05-11"
output: html_document
---

## 0. Available data and code

The data used in this work is from the article of Zhou et al., « Dataset for Monitoring and Visualizing Stroke Rehabilitation Progress using Wearable Sensors (IMU) ». The dataset is available in https://zenodo.org/records/10534055  
The code is available at the address https://github.com/lambertwcamille-source/LAMBERT_CAMILLE.git  

### 1. Scientific problem

### 1.1. Context

The de shape synchrosqueezing transform (dsSST) extracts the instantaneous frequency of a signal by a combination of two non-linear operations, the de shape operation and the synchrosqueezing operation. This reliable technique for extracting the instantaneous frequency of a sustained harmonic walk can be used in future work to extract the period of the walk from the harmonic component of the signal. (Wu et al., 2023)
The application of this technique on the stroke patient stills need to be done. The asymmetric walk and the specificity of the hemiplegic gait can be a limitation in the futur use of this tool.

### 1.2. Research question

The research question behind this work is: Is the detection of walk instantaneous frequency by the deshape synchrosqueezing on acceleration data the same, for sensor position on the wrist in comparison with sensor on the feet for stroke patient who can walk without physical assistance ?

### 1.2. Goal of the work

The goal of this work is to assess the capacity of the dsSST algorithm to find the instantaneous frequency from accelerometer data of a sensor worn on the feet, wrists or sacrum of a stroke patient.

### 1.3. Method

The deshape synchrosqueezing transform is a powerful tool to extract the instantaneous frequency of a sustained harmonic walk from accelerometer data. The pipeline used in this work has been done from the article of Wu et Harezlak, « Application of de-shape synchrosqueezing to estimate gait cadence from a single-sensor accelerometer placed in different body locations ».
Changes have been made to stabilise the short time ceptrum transform with the implementation of a long pass filter. This method is based on the article of Lin et al., « Wave-Shape Function Analysis -- When Cepstrum Meets Time-Frequency Analysis».  


### 1.4. Participant

This work is based on the dataset of Zhou and all. It’s a dataset of 10 stroke patients in an acute phase.  

The inclusion criteria are “To have the cardiorespiratory capacity to walk on a short distance, to don’t have other conditions than stroke who limited the gait”.  

The exclusion criteria are “pronounced chronic obstructive pulmonary disease or heart failure requiring oxygen dependency; knee or hip replacement, orthopaedics injuries or orthopaedic-related pain that impairs gait; pre-existing, severe neuropathy that causes a gait disorder; and gait disorders that are not attributable to a stroke.”  

The patients were monitored during two visits who were spaced for one or two weeks. The first visit was a week after the stoking. In a function of the patient capacity, they had to walk between 60m to 200m in a 10m hallway.  

The patient was monitored by Five IMUs (Xsens DOT, Xsens Technologies B.V., the Netherlands, https://www.xsens.com/wearables/xsens-dot). 

Place on both feet and both wrists and the sacrum (Annexe 1). The IMUs give use the information of triaxial acceleration (range: ± 16 g) and angular velocity (range: ± 1000 degrees/s) with a sampling rate of 120 Hz.  

### 1.5. Results
The results show us that the sensor's location doesn't have a significant impact on the ability to find the instantaneous frequency of the walk with the dsSST algorithm.

## Data organisation

In this directory you have the data of one patient during two visits.
Each visit has 
    _RF:Right foot
    _LF:Left foot
    _RW:Right wrist
    _LW:Left wrist
    _SA:Sacrum
    

# r_movement_analysis_project

From the results of the python_Movement_analysis_project, we are going to analyse the instantaneous frequency found in every sensor. 
  
We have only one patient so we are going to make a Friedman test between the different sensor positions (feet, wrist and sacrum) to see if there is a significant difference in the instantaneous frequency funded by the dsSST algorithm.
  
## Objective

The Goal of this work is the asset the capacity of the dsSST algorithm to find the instantaneous frequency in stroke patient with different sensor position.

The instantaneous frequency is expressed in **Hz**

## Variable types

| Variable                     | Nature                       | Role              |
|:-----------------------------|:-----------------------------|:------------------|
| sensor                       | Qualitative nominal (5 mod.) | Within-subjects   |
| instantaneous frequency (Hz) | Quantitative continuous      | Response variable |
| patient_id                   | Qualitative nominal (ID)     | Statistical unit  |

## Methodology 

The step of the R project are the following:

-Step 1: load the needed package  
  
-Step 2: Load the data 
  
-Step 3: Friedman test between the different sensor position (feet, wrist and sacrum) to see if there is a significant difference between the sensors position.


## Step 1: load the needed package

```{r anova-packages, message=FALSE, warning=FALSE}
# load the need library 

library(tidyverse)
library(irr)

# if neded, install the package 

# install.packages("tidyverse")
# install.packages("irr")


```

## Step 2: Load the data

```{r anova-load}
# Use the normalized path to selection the good directory
project_root <- normalizePath("..")
results_dir  <- file.path(project_root, "results")
frequency_summary<- file.path(results_dir, "frequency_summary.csv")

# load the data frame of the frequency summary
df_frequency_summary <- read_csv(frequency_summary, show_col_types = FALSE)

(df_frequency_summary)
```


## Step 3: Friedman test between the different sensor positions (feet, wrist and sacrum) to see if there is a significative difference between the different sensor positions.

Make a Friedman test quantifies the difference found in each sensors. We selected this test because we have a small sample size and the data is not normally distributed. The Friedman test is a non-parametric test that compares the medians of three or more groups.

Frist we need to reshape the data to have one row per visit and one column per sensor. This will allow us to perform the Friedman test on the peak frequency values for each sensor.

```{r}
# Reshape the data: one row per visit, one column per sensor
wide_data <- df_frequency_summary %>%
  select(visit, sensor, peak_frequency_hz) %>%
  pivot_wider(names_from = sensor, values_from = peak_frequency_hz) %>%
  select(-visit)   # keep only the numeric columns for ICC

wide_data
```

Than we compute the Friedman test

```{r}
# Friedman test : sensors give different frequency ?
friedman_result <- friedman.test(as.matrix(wide_data))
friedman_result

```

## Discussion on the result

We can see that the p-value is 0.5578, which means that there is not a significant difference between the sensors position. 
In the step 2 you can see the same fundamental frequency in every sensor. Only the left wrist a the second visit have a different fundamental frequency but it is not significant.





