---
title: "LAMBERT_CAMILLE_r"
author: "Camille_LAMBERT"
co-authors: "Claude IA and Copilot IA"
date: "2026-03-17"
output: html_document
---

# Statistical analysis of fundamental frequency in patient 0001

From the results of the python_Movement_analysis_project, we are going to analyse the fundamental frequency found in every sensor. 
  
We have only one patient so we are going to make a t-test between the feet and the other sensor (wrist and sacrum) to see if there is a significant difference in the fundamental frequency funded by the dsSST algorithm.
  
## Objective
The Goal of this work is the asset the capacity of the dsSST algorithm to find the fundamental frequency in stroke patient with different sensor position.

The fundamental frequency is expressed in **Hz**

## Variable types

| Variable                     | Nature                       | Role              |
|:-----------------------------|:-----------------------------|:------------------|
| sensor                       | Qualitative nominal (5 mod.) | Within-subjects   |
| fundamental frequency (Hz)   | Quantitative continuous      | Response variable |
| patient_id                   | Qualitative nominal (ID)     | Statistical unit  |

## Methodology 

The step of the R project are the following:

-Step 1: load the needed package  
  
-Step 2: Load the data 
  
-Step 3: T-test between the feet and the other sensor (wrist and sacrum) 



## Step 1: load the needed package

```{r anova-packages, message=FALSE, warning=FALSE}
# load the need library 

library(tidyverse)

# if neded, install the package 

# install.packages("tidyverse")


```

## Step 2: Load the data

```{r anova-load}
# Use the normalized path to selection the good directory
project_root <- normalizePath("..")
results_dir  <- file.path(project_root, "results")
frequency_summary<- file.path(results_dir, "frequency_summary.csv")

# load the data frame of the frequency summary
df_frequency_summary <- read_csv(frequency_summary, show_col_types = FALSE)

(df_frequency_summary)
```


## Step 3: T-test between the feet and the other sensor (wrist and sacrum)
Make a t-test to visualise the difference between the feet and the other sensor (wrist and sacrum). 
Beacause of the few data we have we are going to group the wrist the sacrum in one group and the feet in another group. To enhance the statistical power of the test.

```{r}
## Step 3: T-test between the feet and the other sensors

# Creat the group "feet" (LF, RF) vs "other" (LW, RW, SA)
df_test <- df_frequency_summary %>%
  mutate(
    group = case_when(
      sensor %in% c("LF", "RF")          ~ "feet",
      sensor %in% c("LW", "RW", "SA")    ~ "other",
      )
  )

# T-test (we are going to use the t-test for independent samples because we have only one patient and we want to compare the two groups))
t_test_result <- t.test(
  peak_frequency_hz ~ group,
  data = df_test
)
print(t_test_result)

```
## Discussion on the result

We can see that the p-value is 0.3632, which means that there is not a significant difference between the two groups. 
In the step 2 you can see the same fundamental frequency in every sensor. Only the sacrum a the second visit have a different fundamental frequency but it is not significant.





