---
title: "Main_r"
author: "Camille_LAMBERT"
co-authors: "Claude IA and Copilot IA"
date: "2026-05-11"
output: html_document
---

# Statistical analysis of fundamental frequency in patient 0001

From the results of the python_Movement_analysis_project, we are going to analyse the instantaneous frequency found in every sensor. 
  
We have only one patient so we are going to make a t-test between the feet and the other sensor (wrist and sacrum) to see if there is a significant difference in the instantaneous frequency funded by the dsSST algorithm.
  
## Objective
The Goal of this work is the asset the capacity of the dsSST algorithm to find the instantaneous frequency in stroke patient with different sensor position.

The instantaneous frequency is expressed in **Hz**

## Variable types

| Variable                     | Nature                       | Role              |
|:-----------------------------|:-----------------------------|:------------------|
| sensor                       | Qualitative nominal (5 mod.) | Within-subjects   |
| instantaneous frequency (Hz) | Quantitative continuous      | Response variable |
| patient_id                   | Qualitative nominal (ID)     | Statistical unit  |

## Methodology 

The step of the R project are the following:

-Step 1: load the needed package  
  
-Step 2: Load the data 
  
-Step 3: Friedman test between the different sensor position (feet, wrist and sacrum) to see if there is a significant difference between the sensors position.



## Step 1: load the needed package

```{r anova-packages, message=FALSE, warning=FALSE}
# load the need library 

library(tidyverse)

# if neded, install the package 

# install.packages("tidyverse")


```

## Step 2: Load the data

```{r anova-load}
# Use the normalized path to selection the good directory
project_root <- normalizePath("..")
results_dir  <- file.path(project_root, "results")
frequency_summary<- file.path(results_dir, "frequency_summary.csv")

# load the data frame of the frequency summary
df_frequency_summary <- read_csv(frequency_summary, show_col_types = FALSE)

(df_frequency_summary)
```


## Step 3: Friedman test between the different sensor positions (feet, wrist and sacrum) to see if there is a significative difference between the different sensor positions.

Make a Friedman test quantifies the difference found in each sensors. We selected this test because we have a small sample size and the data is not normally distributed. The Friedman test is a non-parametric test that compares the medians of three or more groups.

Frist we need to reshape the data to have one row per visit and one column per sensor. This will allow us to perform the Friedman test on the peak frequency values for each sensor.

```{r}
# Reshape the data: one row per visit, one column per sensor
wide_data <- df_frequency_summary %>%
  select(visit, sensor, peak_frequency_hz) %>%
  pivot_wider(names_from = sensor, values_from = peak_frequency_hz) %>%
  select(-visit)   # keep only the numeric columns for ICC

wide_data
```

Than we compute the Friedman test

```{r}
# Friedman test : sensors give different frequency ?
friedman_result <- friedman.test(as.matrix(wide_data))
friedman_result
```




## Discussion on the result

We can see that the p-value is 0.5578, which means that there is not a significant difference between the two groups. 
In the step 2 you can see the same fundamental frequency in every sensor. Only the sacrum a the second visit have a different fundamental frequency but it is not significant.





